---
title: "FunctionTrialCodes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Trial Codes For Functions To Test if They Work

You'll find the list of functions being built here before being transformed to the proper package files


## 1. Age Bracket Column Creation
```{r}

library(dplyr)
library(data.table)
data_all <- readRDS("data_all.rds")
data_all_dup <- data_all

View(data_all)


#inefficient code, also if statements do not support vectorized input hence need for lapply, no optimised
agebracket <- function(X){
  if (X < 20){
    Y <- "<20"
  } else
    if (20 <= X & X < 25){
      Y <- "20 - 24"
    }
    else
    if (25 <= X & X < 30){
      Y <- "25 - 29"
    }
    else
    if (30 <= X & X < 35){
      Y <- "30 - 34"
    }
    else
    if (35 <= X & X < 40){
      Y <- "35 - 39"
    }
    else
    if (40 <= X & X < 45){
      Y <- "40 - 44"
    }
    else
    if (45 <= X & X < 50){
      Y <- "45 - 49"
    }
    else
    if (50 <= X & X < 55){
      Y <- "50 - 54"
    }
    else
    if (55 <= X & X < 60){
      Y <- "55 - 59"
    }
    else
    if ( X > 60){
      Y <- "> 60"
    }
 print(return(Y))
}

#inefficient code
agebracket2 <- function(age){
  ifelse (age < 20, Y <- "<20",
    ifelse (age < 25, Y <- "20 - 24",
      ifelse (age < 30, Y <- "25 - 29",
        ifelse (age < 35, Y <- "30 - 34",
          ifelse (age < 40, Y <- "35 - 39",
            ifelse (age < 45, Y <- "40 - 44",
              ifelse (age < 50, Y <- "45 - 49",
                ifelse (age < 55, Y <- "50 - 54",
                  ifelse (age < 60, Y <- "55 - 59", Y <- "> 60")))))))))
                          
 print(return(Y))
}

#function to create age brackets based on input value of age
agebracket3 <- function(age){
  ifelse (age < 20, "<20",
    ifelse (age < 25, "20 - 24",
      ifelse (age < 30, "25 - 29",
        ifelse (age < 35, "30 - 34",
          ifelse (age < 40, "35 - 39",
            ifelse (age < 45, "40 - 44",
              ifelse (age < 50, "45 - 49",
                ifelse (age < 55, "50 - 54",
                  ifelse (age < 60, "55 - 59", "> 60")))))))))
}
#testing
agebracket2(22)
agebracket(55)
a <- agebracket3(98)
a
A <- c(1, 50, 23)
B <- lapply(A, agebracket3)
C <- agebracket3(A)
is.vector(C)




#Function to create a new column
agebracketcol <- function(X){
  X["Age_Bracket"] <- X["Age"] %>% agebracket3() %>% as.vector()
  return(X)
}

#testing on duplicated dataset
data_all_dup <- data_all_dup %>% agebracketcol()
unique(data_all_dup$`Age_Bracket`)
View(data_all_dup)
```

## 2. Age Filter - filter data based on input value of age and its corresponding age bracket
```{r}
agefilter <- function(age, dataset){ #input value of age, dataset is the data to be filtered
  dataset <- agebracketcol(dataset)
  agebracket <- age %>% agebracket3()
  dataset <- dataset %>% filter(Age_Bracket == agebracket)
  return(dataset)
}
#mannual testing
ageb <- (29 %>% agebracket3())
data_all_dup_age_29 <- data_all_dup %>% filter(Age_Bracket==ageb)

#testing the function
data_all_dup_age_29 <- agefilter(29, data_all_dup)
unique(data_all_dup_age_29$Age_Bracket)
View(data_all_dup_age_29)
dim(data_all_dup_age_29)

```
## 3. Overal demographics filter - filter data based on input value of age, gender & nationality
```{r}
#function that deals with missing arguments without breaking
#function broken for unknown reasons, modified below
demographics_filter <- function(dataset, age, gender, nationality){ #demographic data, dataset = raw data
  ifelse(missing(age), 
         ifelse(missing(gender),
                ifelse(missing(nationality),
                       dataset,
                       dataset %>% filter(Country == nationality)),
                ifelse(missing(nationality),
                       dataset %>% filter(M.F == gender),
                       dataset %>% filter(Country == nationality, M.F == gender))),
         
         ifelse(missing(gender),
                ifelse(missing(nationality),
                       dataset %>% filter(Age == age),
                       dataset %>% filter(Age == age, Country == nationality)),
                ifelse(missing(nationality),
                       dataset %>% filter(Age == age, M.F == gender),
                       dataset %>% filter(Age == age, Country == nationality, M.F == gender)))
  )
}
#verified that the ifelse+missing nesting works as expected, not sure why the filter function is not working properly from above
demographics_filter2 <- function(dataset, age, gender, nationality){ #demographic data, dataset = raw data
  ifelse(missing(age), 
         ifelse(missing(gender),
                ifelse(missing(nationality),
                       1,
                       2),
                ifelse(missing(nationality),
                       3,
                      4)),
         
         ifelse(missing(gender),
                ifelse(missing(nationality),
                       5,
                       6),
                ifelse(missing(nationality),
                       7,
                       8))
  )
}
#function still not working, wanna die
demographics_filter3 <- function(dataset, age=NULL, gender=NULL, nationality=NULL){ #demographic data, dataset = raw data
  case_when(
      !age==NULL & !gender == NULL & !nationality==NULL ~ dataset,
      
       age==NULL & !gender == NULL & !nationality==NULL ~ dataset %>% filter(Age == age),
       age==NULL &  gender == NULL & !nationality==NULL ~ dataset %>% filter(Age == age, M.F == gender),
       age==NULL &  gender == NULL &  nationality==NULL ~ dataset %>% filter(Age == age, M.F == gender, Country == nationality),
       age==NULL & !gender == NULL &  nationality==NULL ~ dataset %>% filter(Age == age, Country == nationality),
       
      !age==NULL &  gender == NULL & !nationality==NULL ~ dataset %>% filter(M.F == gender),
      !age==NULL &  gender == NULL &  nationality==NULL ~ dataset %>% filter(M.F == gender, Country == nationality),
       
      !age==NULL & !gender == NULL &  nationality==NULL ~ dataset %>% filter(Country == nationality)
       
    )
}

demographics_filter4 <- function(dataset, age=NULL, gender=NULL, nationality=NULL){ #demographic data, dataset = raw data
  ifelse(is.null(age), 
         ifelse(is.null(gender),
                ifelse(is.null(nationality),
                       dataset,
                       dataset %>% filter(Country == nationality)),
                ifelse(is.null(nationality),
                       dataset %>% filter(M.F == gender),
                       dataset %>% filter(Country == nationality, M.F == gender))),
         
         ifelse(is.null(gender),
                ifelse(is.null(nationality),
                       dataset %>% filter(Age == age),
                       dataset %>% filter(Age == age, Country == nationality)),
                ifelse(is.null(nationality),
                       dataset %>% filter(Age == age, M.F == gender),
                       dataset %>% filter(Age == age, Country == nationality, M.F == gender)))
  )
}

#Success!
demographics_filter5 <- function(dataset, age, gender, nationality){ #demographic data, dataset = raw data
  if(missing(age)) {
    
    if(missing(gender)){
      if(missing(nationality)){
        dataset
      }
      else{
        dataset %>% filter(Country == nationality)
      }
    } else if(missing(nationality)){
      dataset %>% filter(M.F == gender)
    }
    else {
      dataset %>% filter(Country == nationality, M.F == gender)
    }
    
    
    
    
  } else if(missing(gender)){
    if(missing(nationality)){
      agefilter(age, dataset) 
    }
    else{
      agefilter(age,dataset) %>% filter(Country == nationality)
    }
  } else if(missing(nationality)){
    agefilter(age,dataset) %>% filter(Age == age, M.F == gender)
  }
  else{
    agefilter(age, dataset) %>% filter(Age == age, Country == nationality, M.F == gender)
  }
}



data_all_dup <- demographics_filter5(data_all, age=28, gender="M", nationality = "USA")
test <- demographics_filter2(data_all, age = 2, gender = 1, nationality = 1)
test
nationality <- "USA"
age = 25
gender = "M"
dataset <- data_all_dup


data_all_dup <- data_all %>% filter()
dim(data_all_dup)
dim(data_all)
data_all_dup <- data_all %>% filter(Age == age, M.F == gender, Country == nationality)
View(data_all_dup)

```
## 4. Top 10%, Bottom 20%, Global Average - Top 10%
```{r}
#function that only returns the top 10% data points
top10percent <- function(dataset){
  dataset %>% arrange(Official.Time.1) %>% head(round(length(dataset$Official.Time.1)*0.1))
  
}
#testing
data_all_dup_top10 <- top10percent(data_all_dup)
dim(data_all_dup)
dim(data_all_dup_top10)

#function to return a data frame that is plottable using ggplot2
top10percentmean <- function(dataset){
  top10 <- dataset %>% arrange(Official.Time.1) %>% head(round(length(dataset$Official.Time.1)*0.1)) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean time")) %>% t() %>% as.data.frame() %>%  setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Top10"))
  top10$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(top10)[1]<-("milestone(km)")
  return(top10)
}  
test <- top10percentmean(data_all_dup)
test
```
## 5. Top 10%, Bottom 20%, Global Average - Bottom 20%
```{r}
#function to only extract the bottom 20% - no average is calculated
bottom20percent <- function(dataset){
  dataset %>% arrange(desc(Official.Time.1)) %>% head(round(length(dataset$Official.Time.1)*0.2))
  
}
data_all_dup_bottom20 <- bottom20percent(data_all_dup)
dim(data_all_dup)
dim(data_all_dup_bottom20)

names(data_all_dup)
test <- data_all_dup_bottom20[,c(13:22)] %>% lapply(mean)
View(test)

#function to return a data frame that is plottable using ggplot2
bottom20percentmean <- function(dataset){
  bottom20 <- dataset %>% arrange(desc(Official.Time.1)) %>% head(round(length(dataset$Official.Time.1)*0.2)) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>%  setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Bottom20"))
  bottom20$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(bottom20)[1]<-("milestone_km")
  return(bottom20)
}  

test <- bottom20percentmean(data_all_dup)
test
```

## 6. Top 10%, Bottom 20%, Global Average - Global Average
```{r}
globalaverage <- function(dataset){
  global <- dataset %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>%  setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Global"))
  global$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(global)[1]<-("milestone_km")
  return(global)
}
test <- globalaverage(data_all_dup)
test
```
## 6. past time
```{r}
pasttime <- function(pasttime, dataset){
  past_time <- dataset %>% filter(Official.Time.1 > pasttime-7.5 & Official.Time.1 < pasttime+7.5) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>% setDT(keep.rownames=TRUE) %>% mutate(Label = rep("past_time"))
  past_time$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(past_time)[1]<-("milestone_km")
  return(past_time)
}
test <- pasttime(200, data_all_dup)
test

past <- 200
past_test <- data_all_dup %>% filter(Official.Time.1 > past-7.5 & Official.Time.1 < past+7.5) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean)
finalmean <- mean(past_test$Official.Time.1)
finalmean
View(past_test)
```
## 7. Goal time
```{r}
goaltime <- function(goaltime, dataset){
  goal_time_1 <- dataset %>% filter(Official.Time.1 > goaltime-30 & Official.Time.1 < goaltime-15) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>% setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Goal_time_15to30_mins_Faster"))
  goal_time_1$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(goal_time_1)[1]<-("milestone_km")
  
  goal_time_2 <- dataset %>% filter(Official.Time.1 > goaltime-15 & Official.Time.1 < goaltime) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>% setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Goal_time_0to15_mins_Faster"))
  goal_time_2$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(goal_time_2)[1]<-("milestone_km")
  
  goal_time_3 <- dataset %>% filter(Official.Time.1 > goaltime & Official.Time.1 < goaltime+15) %>% mutate(X0K.1 = rep(0)) %>% select("X0K.1", c(13:22)) %>% lapply(mean) %>% as.data.frame() %>% `row.names<-`(c("mean_time")) %>% t() %>% as.data.frame() %>% setDT(keep.rownames=TRUE) %>% mutate(Label = rep("Goal_time_0to15_mins_Slower"))
  goal_time_3$rn <- c(0, 5, 10, 15, 20, 21.10, 25, 30, 35, 40, 42.20)
  colnames(goal_time_3)[1]<-("milestone_km")
  
  goal_time <- rbind(goal_time_1, goal_time_2, goal_time_3)
  
  return(goal_time)
}
test <- goaltime(200, data_all_dup)
test

test %>% ggplot(aes(x=milestone_km, y=mean_time, col=Label))+geom_point()+geom_line()
```
